IOIs Analysis: The Sound of Teaching Music 2

### 2020-05-05 script/RNotebook/articulation.Rmd
edit outline
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Outline - Articulation (KOT, KOR)
## [Experimental Design](#design)

@@

## Main predictions
Participants will exaggerate legato and staccato more while teaching.

>>>>

# Outline - Articulation (KOT, KOR)
## [Experimental Design](#design)
- Main predictions

@@

### Main predictions
Participants will exaggerate legato and staccato more while teaching.

### 2020-05-05 script/RNotebook/dynamics.Rmd
edit outline
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Outline - Dynamics (Key Velocity)
## [Experimental Design](#design)

@@

## Main predictions
- Participants will exaggerate forte and piano more while teaching.
- Participants will make a larger contrast between forte and piano.

>>>>

# Outline - Dynamics (Key Velocity)
## [Experimental Design](#design)
- Main predictions

@@

### Main predictions
- Participants will exaggerate forte and piano more while teaching.
- Participants will make a larger contrast between forte and piano.

### 2020-05-05 script/RNotebook/ioi_1.Rmd
insert the end line
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
edit outline
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Outline - Interonset intervals (IOIs)
## [Experimental Design](#design)

@@

## Main predictions
Participants will play slower while teaching regardless of the skills.

>>>>

# Outline - Interonset intervals (IOIs)
## [Experimental Design](#design)
- Main predictions

@@

### Main predictions
Participants will play slower while teaching regardless of the skills.
